
\red{old text}

Scientific goals:
Connect star formation to galaxy formation: use cosmological simulations to
determine the properties of molecular clouds (particularly magnetic structure),
and then use those molecular clouds as initial conditions for simulations of
star formation (massive star formation?  solar-mass star formation?  both? we
should get a whole range of GMCs…)

It’s impossible to simulate this whole range of scales (cosmic web to
protostellar cores) in a cyclic way (i.e., include all of them in a simulation
lasting a ~Hubble time), so validate sub-grid models for star formation and
feedback that are used at the cosmological/isolated disk simulation scale.

Do first simulations of cosmological galaxy formation using MHD (first?  maybe
not…)(Dolag beat us.)

\citep{Beck12}

We will do cosmology with magnetic fields and see what the galaxies look like.

We will make some star formation things that connect to modern star formation
models, also that include magnetic fields.

We will look at the morphology of the magnetic fields of galaxies.  They'd
better look right.

We will extract some clouds and do some crazy zoom-ins.  This will get us the
right intiial and boundary conditions for mass, magnetic fields, and kinetic
energy.  Dobbs (last week) showed that this might be important.

We will try to see if there's an obvious scale at which the field decouples from
larger/smaller scales.

Our plan is to bridge the theoretical gap between cosmological structure
formation and the formation of stars in Galactic molecular clouds, including a
self-consistent treatment of magnetic fields from cosmological initial
conditions.”  Understanding magnetic field structure at the Galactic scale is
critical for realistic (need better word) simulations of molecular clouds, and
simulating both allows us to constrain our models by both observations of the
interstellar medium in the Milky Way and distant galaxies, and also by examining
molecular clouds in the Local Group. 


\red{Some misc. notes from Dave}

Cosmo sims: 100 pc galaxies

Pull one out: molecular cloud formation

Galactic scales:
Does B affect the lifetime of MC in the disk
How does this evolve with Z
What impact does SF model have on SFR, IMF
Does seed field affect the detailed structure of the B. Beck, Beck, Beck, Eggs,
Sausage and Beck (not much Beck in that)v
B field, mach number distribution in MCs.
