\emph{TODO and jots}
TO DO
\begin{enumerate}
\item resolution
\item three models
\item Cite vazza
\end{enumerate}

JOTS
\begin{enumerate}
\item Thread Safe Proposal Writing.
\item We will use these results in other coordinated work on the CMB
Foregrounds.
\item Two major questions
\item Run some cosmology simulations for the merger history and initial and
boundary conditions.
\item We will focus on how, when, and where magnetic fields are produced in
galaxies.  
\item Our primary focus will be $L^*$ galaxies like the Milky Way, but other
science will be enabled.
\item It is clear that magnetic fields are assembled early in the lifetime of
the galaxy, so it is necessary to begin with cosmic dawn.
\item However we also want to really see the structure, so we need to do high
resolution simulations.
\item It is less clear how far into the halo the magnetic fields can persist,
and the synchrotron may come from very high up.
\item Observations will focus on the distribution of synchrotron gas and
polarized dust emission.
\item A nice side project would be to fit the \citet{Jansson12} model.
\item We will use Enzo and Enzo-E in order to achieve resolution necessary.
\item Magnetic field can be produced by 1.) flux freezing 2.) accretion with
progenitor galaxies 3.) large scale dynamo 4.) small scale dynamo 5.) Seeding by
stellar explosions.  There are likely other battery mechanisms.
\item Molecular clouds are not likely going to be influenced directly by the
halo, but the scale at which molecular clouds decouple from the ISM is not at
all clear.  
\end{enumerate}
